Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-01-26 Draft/introduction.tex
Remove usepackage{siunitx} as it seems not be a default package. Replace in the introduction TeV

The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \SI{8}{\tera\electronvolt} data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \SI{13}{\tera\electronvolt} data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.

>>>>

The process with two positively charged W bosons is the VBS process with the largest signal-background ratio at the LHC, for which evidence has been found in \TeV data~\cite{Aad:2014zda,Khachatryan:2014sta} and which is now started to be observed~\cite{Sirunyan:2017ret} and measured~\cite{Aaboud:2016ffv} in \TeV data.
For now the measurements of VBS processes are limited by statistics but the situation will change in a near future.
On the theoretical side, it is thus of prime importance to provide precise predictions and infer their related systematic errors.
